### 2011-06-03 docs/pubs/EIM-2011/annotation.tex
resolve section references from intro.tex to other .tex files
OBOE/Annotation figure for Kelp CHN dataset. needs better caption

\section{Annotation}

@@

The Annotation structure largely mirrors the core classes in OBOE. Observations are composed of Measurements of a specific Entity and are represented by a collection of Characteristics (usually just one) collected using a defined Protocol and Standard (i.e. unit). 
Tablular data object attributes are mapped to a Measurement such that a collection of attributes usually pertain to the Entity of a shared Observation. These Observtions can provide context for other Observations such that the structure of the observational data model and collection paradigm are formally represented in the Annotation.

>>>>

\section{Annotation}
\label{sec:annotation}

@@

The Annotation structure largely mirrors the core classes in OBOE. Observations are composed of Measurements of a specific Entity and are represented by a collection of Characteristics (usually just one) collected using a defined Protocol and Standard (i.e. unit). 
Tablular data object attributes are mapped to a Measurement such that a collection of attributes usually pertain to the Entity of a shared Observation (\figref{fig:kelp-mass-model}). These Observtions can provide context for other Observations such that the structure of the observational data model and collection paradigm are formally represented in the Annotation.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/kelp-mass-model.png}
\caption{Partial OBOE Annotation for Kelp sampling data. Shaded nodes represent ontological concepts; rectangular nodes are data table attibutes mapped to OBOE characteristics.}
\label{fig:kelp-mass-model}
\end{figure}
